Optimal (Multiway) Spatial Joins

### 2024-06-04 msj.tex

First, we will prove $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$ or equivalently: if a segment $h \in \dcross_H(\bm{t})$, then $h$ crosses $r^*$. To do so, we need to explain why $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1,$ $\maxtop(r')]$.
\begin{itemize}
    \item The fact of $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $\gbot(\bm{t})$, which is $r'$. As the x-range of $r'$ is $[x_1,x_2]$, it must hold true that $\xleft(h) < x_1 \le x_2 < \xright(h)$.

@@

Second, assuming that the segments of $\cross_H(r^*)$ are sorted in ascending order of their y-coordinates,
we will prove that $\dcross_H(\bm{t})$ includes a prefix of the sorted order. It suffices to establish the following equivalent claim:

@@

\item We first show that $h$ crosses $r'$, or equivalently: $\xleft(h)  < x_1 \leq x_2 < \xright(h)$ and $y_h \in [y_1, y_2]$. These conditions hold true because $h$ crosses $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$, and $\maxtop(r')\leq y_2$ (due to the definition of a top-sliced rectangle in \eqref{eqn:hv:type1:topsliced}).

>>>>

We will first prove $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$ or equivalently: if a segment $h \in \dcross_H(\bm{t})$, then $h$ crosses $r^*$. To do so, we need to explain why $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1,$ $\maxtop(r')]$.
\begin{itemize}
    \item The fact of $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $\gbot(\bm{t})$, which is $r'$. As the x-range of $r'$ is $[x_1,x_2]$, it must hold true that $\xleft(h) < x_1 \le x_2 < \xright(h)$.

@@

Next, assuming that the segments of $\cross_H(r^*)$ are sorted in ascending order of their y-coordinates,
we will prove that $\dcross_H(\bm{t})$ includes a prefix of the sorted order. It suffices to establish the following equivalent claim:

@@

\item We first show that $h$ crosses $r'$, or equivalently: $\xleft(h)  < x_1 \leq x_2 < \xright(h)$ and $y_h \in [y_1, y_2]$. These conditions hold true because (i) $h$ crosses $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$, and (ii) the definition of a top-sliced rectangle in \eqref{eqn:hv:type1:topsliced} tells us $\maxtop(r')\leq y_2$.
